\subsection{Design constraints}
\subsubsection{Standards compliance}
The privacy is one of the most important characteristic which the system has to implement. The agreement, shown at sign up operation for both user and third party, must be written in a way that are in compliance with the law. Of course, it also has to protect the privacy of people and what the application does, must not violate what is written in the agreement. Furthermore, the APIs, used to implement the functionality about maps, text-to-speech, voice recognition and so on, must respect the license defined by the external services. For instance, using an API which is open source is completely compliant with the law. 

\subsubsection{Hardware limitations}
The hardware limitations of the application are strict for the user. Infact, he needs two devices, and the second one is not so wide-spread:
\begin{itemize}
\item A smartphone, for being connected to the TrackMe system. This allow him to accept or refuse requests from third party customer, enroll in available runs and spectate races. The smarthphone required, needs an Internet connection, used for communicating with the system. \\ 
Furthermore, it needs GPS and NFC sensors.  
\item A device provided of at least a NFC sensor: this will collect health status of the user and will communicate with the smarthphone. The data detection and the communication must be performed in a fast way (see performance requirements)
\end{itemize}

For what concerns the hardware limitations of the third party customers, they are not strict at all. They only needs a smartphone that can access to the Internet in order to send requests and access information.

