\subsection{Scenarios}

\subsubsection{Scenario 1}
The company Canpari, whose business regards the production of natural and herbal medicines, needs data on the health statuses, during last year, of the inhabitants of Milan. This will allow them to evaluate the project of opening their first shop in the city. \\
Therefore, with their Data4Help account, the marketing office compiles and sends an aggregated request for accessing the needed information. 
Once that the demand is received, the system analyses it: since there are, of course, more then a thousand of user subscribed in Milan, the requests is approved and the access is granted to Canpari. 

\subsubsection{Scenario 2}
The company Tibaldi\&Zhou has set up a shocking outdoor art show that will take place in the following two months in Piazza Duomo.
Therefore, it is interested in having access to data regarding the health statuses of the user that visit this location when they are close to the exhibition.
This is necessary in order to monitor the public feedback, using the heart rate of possible spectators. \\
In order to accomplish this purpose, they subscribes, using Data4Help, to the mentioned above future data: when the two months will pass by, the system will evaluate the anonymisation constraint. Since there will have been, of course, at least 1000 user that pass from Piazza Duomo, the access will be provided to the company. 

\subsubsection{Scenario 3}
Jacob is preparing for a marathon and, while training, he always keeps with him his device with the application installed. 
Unfortunately, yesterday he had an hearth attack while running, but his device was able to detect the health parameters below the threshold and have suddenly called the nearest hospital. \\
Once the call had been picked up, the device has communicated autonomously to the emergency room operator the observed health status and the location of the user, in order to request for an ambulance. 
Since, the operator understood the dangerous situation, he has accepted the demand and sent an ambulance to the location.

\subsubsection{Scenario 4}
The Company Like wants to organize a public run in Milan and it assigns this task to Mattia, who is the chief of the public relations office. \\
Therefore, Mattia opens the TrackMe's application and fill the form for submitting a new run event. 
More specifically, he defines the name of the run, its path, the date and the time in which the run will start, and a closure date for the subscriptions. 
Furthermore, he also specifies 10 as the minimum number of people that needs to be present.

\subsubsection{Scenario 5}
Tang-Tang and his 9 friends are amateur runners that want to join a run in order to get some fun. 
Therefore, they decide to enroll, before the expiration date, in a run, whose minimum number of athletes is 10, organized by Abibas on the 5th of November. \\
When the expiration date arrives, the system checks the constraints on the number of runners. 
Since this constraint is satisfied, they wait for the day of the event: at this point they race and, at the end of the competition, Tang-Tang is announced as the winner. 

\subsubsection{Scenario 6}
Harry, who use the TrackMe application daily, keeps receiving everyday individual requests an Indian company and he continues to refuse.\\
Finally, one day, he decides to block requests from that company: he won't see any spam demand anymore and the access is, of course, not granted. 

\subsubsection{Scenario 7}
Xiang, who is very concerned about his health status, pays a private company for analyzing all of his health status data. \\ 
In order to accomplish this, he receives an individual request from them and he accepts it: as soon as he does, the company has access to the needed information.

\subsubsection{Scenario 8}
Riccardo receives a not desired request to access his individual data by an unknown company. 
He thinks that probably a mistake has taken place when performing the demand, and, therefore he just refuses. 
In this way, it won't be possible for them to access Riccardo's information.

\subsubsection{Scenario 9}
Giulio is very worried about his old father, Franco, and, therefore, convinces him to use the TrackMe application: in this way, he can send him a request to access his data, and keep the situation under control. \\
Franco, according to the deal, registers to the service: he provides identification data, social security number and a password. 
The system checks that an account associated with identification information and social security number does not exists: since this constraint is satisfied, the registration happens without any problem.  

\subsubsection{Scenario 10}
Matteo, who is already a TrackMe user, has recently bought a new phone.
Therefore, since he wants to keep using the application, he needs to perform the login.\\
To reach this goal, he provides his identification data and the password: since he types both of them correctly, the access to the application is performed. 
