\section{Acceptance tests}
The approach to acceptance testing, for both data for help and automated SOS, has been
conducted in the following way. 
First of all, it has been decided to test all the possible use cases that are described in the
second version of the requirements and analysis document (of course, only the scenarios that
regards the implemented requirements and goals, mentioned in the implementation and document testing, have been considered). \\
The exceptions of the various use cases have been considered too, since the system should
behave properly, also, in these conditions. \\
Secondly, the website has been tested manually, by exploring the UI and its possibilities. \\

The tests that regards the user cases have been performed with JMeter. The source code is present in the delivery folder. 
Before starting the testing phase it is necessary to know the structure of the json files that are sent to the server. To do this you can use
one of the JMeter features and create a Test Script Recorder. HTTP(S) Test Script Recorder can be used to record all the requests which web
application is making to server. As the name suggests, it will capture only the HTTP(s) requests. It can also use grouping option in this
recorder to organize the requests in such a way that similar requests are stored together.(i.e. in the source code, in Thread group section
all the message are stored) Add URL patterns in include and exclude list as per your requirement. In such way is possible to know how are
structured the request and then is possible to create some one of new for testing.

\par
The cases are presented in the next two subsections, each of which first exposes the
tests performed on the use cases divided by goal. After that, the manual tests on the UI are presented. \\
Finally, at the end of this chapter, it is possible to find some brief conclusions. 

\input{testcases/d4htests}
\input{testcases/asostests}
\input{testcases/conclusions}
